Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-28 datapaper_calibration.tex
explant conlusion
albedo definition

The depth noise $\varepsilon$ is modeled as the sum of an image dependent term $\varepsilon_I$ and a sensor dependent term $\varepsilon_S$:
\begin{equation}
\varepsilon = \varepsilon_I + \varepsilon_S. \label{eq:epsilon}
\end{equation}
The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.
On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.
The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
In our experiments we observed a flat, uniform albedo surface (\todo{Danial: Please define ``albedo" here as from Comment $38$}) perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
Object depth, $d$, has a large impact on $\varepsilon_I$.
For constant depth, we observed that the primary factor affecting the variance is the pixel radius $r$, from the image center.
Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.
From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.

@@

\begin{table*}
\begin{center}
\caption{Plant image resolution of Arabidopsis and Bean databases, computed based on the yellow ROIs in Figure~\ref{fig:fourmodality}.}
\label{tab:resolution}
\begin{tabular}{c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & fluorescence & IR & RGB & depth \\
\hline
Arabidopsis & $\sim$$240\times240$ & $\sim$$240\times240$ & $\sim$$120\times120$ & $\sim$$25\times25$ \\
%\hline
Bean & $1,000\times640$ & $1,000\times640$ & $380\times720$ & $90\times190$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

The depth noise $\varepsilon$ is modeled as the sum of an image dependent term $\varepsilon_I$ and a sensor dependent term $\varepsilon_S$:
\begin{equation}
\varepsilon = \varepsilon_I + \varepsilon_S. \label{eq:epsilon}
\end{equation}
The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.
On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.
The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images.
In our experiments we observed a flat, uniform albedo (the ratio of reflected light to incident light) surface perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images.
Object depth, $d$, has a large impact on $\varepsilon_I$.
For constant depth, we observed that the primary factor affecting the variance is the pixel radius $r$, from the image center.
Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis.
Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.
From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.

@@

\begin{table*}
\begin{center}
\caption{Plant image resolution of Arabidopsis and Bean databases, computed based on the yellow ROIs in Figure~\ref{fig:fourmodality}.}
\label{tab:resolution}
\begin{tabular}{c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & Fluorescence & IR & RGB & Depth \\
\hline
Arabidopsis & $\sim$$240\times240$ & $\sim$$240\times240$ & $\sim$$120\times120$ & $\sim$$25\times25$ \\
%\hline
Bean & $1,000\times640$ & $1,000\times640$ & $380\times720$ & $90\times190$ \\
\hline
\end{tabular}
\end{center}
\end{table*}
